---
title: "Compute Relative Ordinals Demo"
author: "Sarah Gripshover"
date: "October, 2016"
output: 
  html_document:
    fig_caption: no
    toc: yes
    theme: spacelab
    css: https://raw.githubusercontent.com/PERTS/gymnast/master/Rmd/rmd_styles.css
---


# Purpose

The `compute_relative_ordinals` module in perts_analyses is used to generate 
ordinal values relative to a reference value. The main use case is computing 
the number of terms (or years, etc.) that have passed since 
each subject in a dataset completed 
an intervention.

# Load Gymnast 
```{r, results='hide', message=FALSE, warning=FALSE}

options(stringsAsFactors = FALSE)
github_base_path <- "~/Sites/perts_analyses/common/"

tryCatch({
    source("~/Sites/gymnast/R/util.R", chdir = TRUE)
    source("~/Sites/gymnast/R/util_qualtrics_cleaning.R", chdir = TRUE)
    source("~/Sites/gymnast/R/util_graphing.R", chdir = TRUE)
}, error = function(e){
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_legacy.R")
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_qualtrics_cleaning.R")
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_graphing.R")
})

source("~/Sites/perts_analyses/common/compute_relative_ordinals.R")

opts_chunk$set(results = "asis")

```

# Load sample data

```{r}

demo_folder <- github_base_path %+% "Rmd/compute_relative_ordinals_demo/"

d1 <- read.csv(demo_folder  %+% "sample_data1.csv")
reference_ordinals1 <- read.csv(demo_folder %+% "reference_ordinals1.csv")

d2 <- read.csv(demo_folder  %+% "sample_data2.csv")
reference_ordinals2 <- read.csv(demo_folder %+% "reference_ordinals2.csv")
timetable2 <- read.csv(demo_folder %+% "time_table_2.csv")

```

# Example 1: an ordered time variable

## check out the data

`d1` is a data.frame with an ordinal time variable. In most cases, 
this will be a variable corresponding to academic terms or academic 
years. In `d1`, the term variable has a year component and an 
ordinal component within the year (e.g., "2014_1" is the first 
term in AY 2014-15).

```{r}
util.print_pre(d1)
```

`reference_ordinals` is a data.frame with 1 row per id value 
that shows what each subject's reference time is. This reference 
time usually corresponds to the term in which students completed 
an intervention activity, or matriculated.

```{r}
util.print_pre(reference_ordinals1)
```

`compute_relative_ordinals` can then be used to assign an ordinal value 
for all the values in the term column, relative to each particular subject's 
reference time. Zero corresponds to the time value in which the reference 
event took place for each subject, negative numbers correspond to times 
before the reference event, and positive numbers correspond to times after 
the reference event.

## compute relative ordinals

`compute_relative_ordinals` takes 4 arguments:

* `time_column` is a vector of data representing
some time-dependent thing (e.g., terms, years). 
In this case is the `term` column in `d1`
* `id_column` is a vector of the same length as `time_column` 
indicating subject id values (e.g., student ID). In this case, 
it's the `subject` column in `d1`.
* `subject_reference_time_table` is a 2-column table where one
field contains unique id values and the other contains values
of time_column relative to which the relative ordinals
should be computed (e.g., the name
of the term in which an intervention took place.) The
column names of this table MUST be 'id' and 'reference_time'. In 
this case, it's the `reference_ordinals1` data.frame.
* `ordered_timeline` is a vector containing ALL of the expected 
values in `time_column`, sorted in ascending order of time. In this 
case, we create `ordered_timeline` below as `timeline1`.

```{r}
d1$rel_term <- compute_relative_ordinals(d1$term, d1$subject, reference_ordinals1)
util.print_pre(d1)
```

You can then go on to do whatever you want, for example, computing a 
"pre-intervention" column:

```{r}
d1$pre <- d1$rel_term < 0
util.print_pre(d1)
```

Note that becuase the inputs to `compute_relative_terms` are vectors, rather 
than, say, column name strings and a data.frame, it can be used seamlessly
in dplyr pipes:

```{r}
d1 %>%
    mutate(rel_term_dplyr = compute_relative_ordinals(term, subject, reference_ordinals1)) %>%
    util.print_pre()
```

# Example 2: an un-ordered time variable

## An un-sorted time variable

Sometimes you have schools with whacky terms that just aren't sortable.
For example, Kaplan had some crazy term labels like 1401B and 1401A, 
where 1401B comes BEFORE 1401A. For a case like this, you'd want 
to use the `ordered_timeline` parameter.

First, note that we made a .csv that gives each term label and its 
ordinal value in the Kaplan scheme:

```{r}
util.print_pre(timetable2)
```

## Check out the data

And now let's look at the data:

```{r}
util.print_pre(d2)
util.print_pre(reference_ordinals2)
```

## Compute relative terms

We can compute relative terms by using the timetable as a timeline. 
We'll just convert the 2-column table to a single, sorted vector first.

```{r}
# first, sort the values into a timeline
timeline2 <- timetable2$term_code[timetable2$term_ordinal]
d2$rel_term <- compute_relative_ordinals(d2$term, d2$subject, reference_ordinals2, timeline2)
util.print_pre(d2)
```