---
title: "2019 CL EP analysis.Rmd"
author: "Daniel Greene"
date: '`r format(Sys.time(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: yes
    fig_width: 9
    fig_height: 7
    fig_caption: yes
  html_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 9
    toc_depth: 2  
---

# Summary

This document analyzes relationships between student learning conditions and math course GPA during the 2019 school year.

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

```

```{r, include=FALSE}

############### USER-DEFINED INPUTS #####################################

general_data_folder_crypt_path <- "SY 2018-19 Q4"
input_data_crypt_path <- "SY 2018-19 Q4/2018-2019 CL cleaned data for PERTS analysis.csv"

```

```{r, results='hide', echo = FALSE}

############### LOAD LIBRARIES AND PATHS #####################################

options(stringsAsFactors = FALSE)
options(xtable.comment = FALSE)
github_base_path <- "https://raw.githubusercontent.com/PERTS/gymnast/master/"

tryCatch({
    source("~/Sites/gymnast/R/util.R")
    gymnast_install()
    library(tidyverse)
    source("~/Sites/gymnast/R/util_data_summaries.R")
    source("~/Sites/gymnast/R/util_qualtrics_cleaning.R")
    source("~/Sites/gymnast/R/util_graphing.R")
    source("~/Sites/gymnast/R/util_scale_computation.R")
    source("~/Sites/gymnast/R/util_dfc.R")
}, error = function(e){
    source(github_base_path %+% "R/util.R")
    gymnast_install()
    source(github_base_path %+% "R/util_data_summaries.R")
    source(github_base_path %+% "R/util_qualtrics_cleaning.R")
    source(github_base_path %+% "R/util_graphing.R")
    source(github_base_path %+% "R/util_scale_computation.R")
    source(github_base_path %+% "R/util_dfc.R")
})

library(tidyverse)
library(lubridate)
library(kableExtra)
library(scales)
library(corrplot)
library(egg)

# Set "today" - by default, use the real today
TODAY <- lubridate::ymd(Sys.Date())

REPO <- "~/Sites/analysis/Engagement Project 2018-19/2018-2019 CL EP analysis /"

```

```{r}

############### LOAD DATA #####################################

d <- util.find_crypt_paths(list(a = input_data_crypt_path))$a %>%
  read.csv()

d$q4_math_course_id <- as.factor(d$q4_math_course_id)

# make a few more handy vars
d$lcs_good <- d$comb_lc_score >= 6
d$marginalized <- (d$black | d$hispanic | d$amindian | d$pacisl | d$multirace) %>%
  util.recode(c(FALSE, TRUE),
              c("White/Asian", "Black/Hispanic/AmIndian/PacIsl/Multi"))

# Sanity check data
# d %>%
#   select(one_of(c("tc1_2", "tc2_2", "tc4_2", "fg2_2", "fg3_3", "mw1_2", "mw2_2", "mw3_2"))) %>%
#   View

```

# Confirmatory analyses

## H1: Combined LC score predicts Q4 math grade.

```{r}

lc_grade_cor_test <- cor.test(d$q4_math_grade, d$comb_lc_score)
# lc_grade_cor_test

```

Learning conditions positively correlated with Q4 math grades (r = `r round(lc_grade_cor_test$estimate, 2)`, p < .001).

# Exploratory analyses

## Do LCs still predict grades when controlling for demographics? Yes.

```{r, warning=FALSE, results='asis'}

lm(q4_math_grade ~ comb_lc_score + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
             frpl + ell + iep + ese,
           data = d) %>%
  stargazer(star.cutoffs = c(.05, .01, .001),
          notes        = "1 star p<.05; 2 stars p<.01; 3 stars p<.001",
          notes.label  = "",
          notes.append = FALSE,
          single.row=TRUE,
          header=FALSE,
          title = "LCs still predict Q4 math grades when controlling for demographics")

```

\newpage

## Do individual LCs each predict grades in separate regressions? Yes.

```{r, results='asis'}

# tc - yes (bigger effect)
tc_mod <- lm(q4_math_grade ~ tc + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
             frpl + ell + iep + ese,
           data = d)
# fg - yes
fg_mod <- lm(q4_math_grade ~ fg + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
             frpl + ell + iep + ese,
           data = d)
# mw - yes
mw_mod <- lm(q4_math_grade ~ mw + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
             frpl + ell + iep + ese,
           data = d)

stargazer(tc_mod, fg_mod, mw_mod,
        star.cutoffs = c(.05, .01, .001),
        notes        = "1 star p<.05; 2 stars p<.01; 3 stars p<.001",
        notes.label  = "",
        notes.append = FALSE,
        single.row=TRUE,
        header=FALSE,
        title = "Individual LCs each predict Q4 math grade in separate regressions")

# graphing
d_m <- melt(d,
            id.vars = c("student_id", "q4_math_grade"),
            measure.vars = c("fg", "mw", "tc"))
ggplot(d_m,
       aes(value, q4_math_grade, color = variable)) +
  geom_smooth() +
  xlab("Learning condition value (1-7)") +
  ylab("Q4 Math GPA (0-4)") +
  ggtitle("Relationships between individual learning conditions and Q4 math grades")

# Should I include these covariates all together if they are intercorrelated highly?
# cor( d[, c("tc", "fg", "mw")], use="pairwise" ) %>%
#     corrplot( type="lower", method = "number", tl.col = "black")
# No - they are all intercorrelated at least .57.

```

\newpage

## Do LCs still predict grades when also controlling for non-math GPA? Then comb_lc_score is only marginally significant.

But presumably we are controlling away a lot of unique student-teacher interaction here.

```{r, results='asis'}

lm(q4_math_grade ~ comb_lc_score + q4_non_math_gpa + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
             frpl + ell + iep + ese,
           data = d) %>%
  stargazer(star.cutoffs = c(.05, .01, .001),
          notes        = "1 star p<.05; 2 stars p<.01; 3 stars p<.001",
          notes.label  = "",
          notes.append = FALSE,
          single.row=TRUE,
          header=FALSE,
          title = "LCs only marginally predict Q4 math grades when controlling for non-math GPA")

```

\newpage

## What if we include random effects of course and school?

LMER drops "multirace" and "ese" fixed effect categories as "rank deficient", then finds no relationship.
But presumably we are controlling away classroom culture here, so that makes sense.

```{r, results='asis'}

lc_lmer_mod <- lmer(q4_math_grade ~ comb_lc_score + q4_non_math_gpa + gender + 
                      white + black + asian + hispanic + amindian + pacisl + multirace + 
                      frpl + ell + iep + ese + (1 | q4_math_course_id) + (1 | school),
           data = d)
class(lc_lmer_mod) <- "lmerMod"
stargazer(lc_lmer_mod,
          star.cutoffs = c(.05, .01, .001),
          notes        = "1 star p<.05; 2 stars p<.01; 3 stars p<.001",
          notes.label  = "",
          notes.append = FALSE,
          single.row=TRUE,
          header=FALSE,
          title = "LCs do not predict Q4 math grades when controlling for course and school")

```

\newpage

## What if we include previous math GPA? (Don't have those vars on-hand yet.)

## What is coefficient alpha for LCs in this dataset? (About .9.)

```{r}

lc_qs <- c("tc1_2", "tc2_2", "tc4_2",
           "fg2_2", "fg3_2",
           "mw1_2", "mw2_2", "mw3_2")
my_alpha <- psych::alpha(d[, lc_qs])$total$std.alpha %>% round(2)

```

Confirmed: Cronbach's alpha = `r my_alpha`.

## Do LCs predict attendance and disciplinary outcomes? (No.)

```{r, results='asis'}

# Q4 absences: No
# ggplot(d, aes(q4_unex_absences)) + geom_histogram() Note - not normally distributed
lm(q4_unex_absences ~ comb_lc_score + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
             frpl + ell + iep + ese,
           data = d) %>%
  stargazer(star.cutoffs = c(.05, .01, .001),
          notes        = "1 star p<.05; 2 stars p<.01; 3 stars p<.001",
          notes.label  = "",
          notes.append = FALSE,
          single.row=TRUE,
          header=FALSE,
          title = "LCs do not predict unexcused-absence rate (using a standard linear model)")

# Trying Poisson regression: Nope.
# summary(glm(q4_unex_absences ~ comb_lc_score + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
#              frpl + ell + iep + ese,
#             family = "poisson",
#            data = d))

# for binary outcome?
# d$q4_unex_absences_any <- d$q4_unex_absences > 0
# summary(glm(q4_unex_absences_any ~ comb_lc_score + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
#              frpl + ell + iep + ese,
#             family = binomial,
#            data = d))

# What about Q4 attendance rate, or having a 96%+ attendance rate for Q4? Nope.
# summary(lm(prop_q4_present ~ comb_lc_score + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
#              frpl + ell + iep + ese,
#            data = d))
# summary(glm(q4_present_high ~ comb_lc_score + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
#              frpl + ell + iep + ese,
#             family = binomial,
#            data = d))



# Q4 suspensions:
# ggplot(d, aes(q4_suspensions)) + geom_histogram() Heavily lopsided, so make binary
d$q4_suspensions_any <- d$q4_suspensions > 0
# summary(glm(q4_suspensions_any ~ comb_lc_score + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
#              frpl + ell + iep + ese,
#             family = binomial,
#            data = d)) # Error
# summary(glm(q4_suspensions_any ~ comb_lc_score,
#             family = binomial,
#            data = d)) # Nothing

glm(q4_suspensions_any ~ comb_lc_score + gender + marginalized +
             frpl + ell + iep,
            family = binomial,
           data = d) %>%
  stargazer(star.cutoffs = c(.05, .01, .001),
          notes        = "1 star p<.05; 2 stars p<.01; 3 stars p<.001",
          notes.label  = "",
          notes.append = FALSE,
          single.row=TRUE,
          header=FALSE,
          title = "LCs do not predict having >0 Q4 suspensions")


```

\newpage

## Understanding group differences in specific LCs

On average, marginalized students report higher LCs than non-marginalized students. But in this sample, it only shows up in Meaningful Work and (to a lesser extent) Feedback for Growth, not in Teacher Caring. Gender differences are minimal.

```{r}

# All LCs
# ggplot(d,
#        aes(marginalized, comb_lc_score, fill = gender)) +
#   geom_bar(stat = "summary", fun.y = "mean", position = position_dodge()) +
#   ug.se_error_bar

# Individual LCs
d_m <- melt(d,
            id.vars = c("student_id", "marginalized", "gender"),
            measure.vars = c("fg", "mw", "tc"))
ggplot(d_m,
       aes(marginalized, value, fill = gender)) +
  geom_bar(stat = "summary", fun.y = "mean", position = position_dodge()) +
  ug.se_error_bar +
  facet_grid(. ~ variable) +
  ggtitle("Group differences in learning-condition scores")

```


\newpage

## Are LC relationships with outcomes moderated by race, gender, or reduced-price lunch status? (No - see Rmd for details.)

```{r}
# 
# # Nothing with gender
# summary(lm(q4_math_grade ~ comb_lc_score*gender + white + black + asian + hispanic + amindian + pacisl + multirace +
#              frpl + ell + iep + ese,
#            data = d))
# 
# # Nothing with FRPL
# summary(lm(q4_math_grade ~ comb_lc_score*frpl + gender + white + black + asian + hispanic + amindian + pacisl + multirace +
#             ell + iep + ese,
#            data = d))
# 
# # Nothing with marginalized bucket-category
# summary(lm(q4_math_grade ~ comb_lc_score*marginalized + gender + frpl +
#             ell + iep + ese,
#            data = d))
# # Hispanic stands out in simple analysis, so try moderation on that? Nothing.
# summary(lm(q4_math_grade ~ comb_lc_score*hispanic + white + black + asian + gender + amindian + pacisl + multirace +
#              frpl + ell + iep + ese,
#            data = d))
# 
# # Graph suggests that there IS an interaction for a binary "lcs_good" variable...
# ggplot(filter(d, !is.na(lcs_good)),
#        aes(lcs_good, q4_math_grade)) +
#   geom_bar(stat = "summary", fun.y = "mean") +
#   ug.se_error_bar +
#   facet_grid(gender ~ marginalized) +
#   ggtitle("Higher LCs appear to predict higher math grades for marginalized students of all genders")
# # ...but this is not supported by linear models?!
# summary(lm(q4_math_grade ~ lcs_good*marginalized,
#            data = d))
# summary(lm(q4_math_grade ~ lcs_good*marginalized + gender + frpl +
#             ell + iep + ese,
#            data = d))


############## Exploratory analyses of this relationship by race
# ggplot(d,
#        aes(comb_lc_score, q4_math_grade)) +
#   geom_smooth()
# 
# d$earned_abc <- as.numeric(d$q4_math_grade >= 2)
# d$lc_good <- as.numeric(d$comb_lc_score >= 6)
# 
# ggplot(d,
#        aes(comb_lc_score, earned_abc)) +
#   geom_smooth()
# 
# ggplot(d,
#        aes(lc_good, q4_math_grade)) +
#   geom_bar(stat = "summary", fun.y = "mean") +
#   ug.se_error_bar +
#   facet_grid(. ~ marginalized)
# 
# table(d$marginalized)
# 
# table(d$marginalized, d$lc_good)
# table(d$hispanic, d$lc_good)
# 
# ggplot(d,
#        aes(lc_good, q4_math_grade)) +
#   geom_bar(stat = "summary", fun.y = "mean") +
#   ug.se_error_bar +
#   facet_grid(. ~ hispanic)
# 
# ggplot(d,
#        aes(lc_good, q4_math_grade)) +
#   geom_bar(stat = "summary", fun.y = "mean") +
#   ug.se_error_bar +
#   facet_grid(. ~ white)
# 
# ds.summarize_by_column(d[, c("white", "asian", "black", "hispanic", "amindian", "pacisl", "multirace")])
# 
# ggplot(d,
#        aes(lc_good, earned_abc)) +
#   geom_bar(stat = "summary", fun.y = "mean") +
#   ug.se_error_bar

```




# For external report 

```{r}
alpha <- psych::alpha(d[c("tc1_2", "tc2_2", "tc4_2", "fg2_2", "fg3_2", "mw1_2", "mw2_2", "mw3_2")])
alpha$total %>%
    xtable()
d$lc_agree_disagree <- ifelse(d$comb_lc_score >= 5, "Positive conditions", "Negative conditions") %>%
    factor(levels = c("Negative conditions", "Positive conditions"))
d$lc_agree_disagree_numeric <- ifelse(d$lc_agree_disagree %in% "Positive conditions", 1, 0)
d$A_or_B <- ifelse(d$q4_math_grade >= 3, 1, 0)
d$C_or_better <- ifelse(d$q4_math_grade >= 2, 1, 0)
d$D_or_better <- ifelse(d$q4_math_grade >= 1, 1, 0)

cor.test(d$A_or_B, d$lc_agree_disagree_numeric)



d %>%
  dplyr::filter(complete.cases(d)) %>%
  group_by(floor(comb_lc_score)) %>%
  summarise(
    n = n(),
    grade_points = mean(q4_math_grade, na.rm = TRUE),
    A_or_B = mean(q4_math_grade >= 3),
    C_or_better = mean(q4_math_grade >= 2)
  )



d$lc_bin <- floor(d$comb_lc_score)# %>%
  #factor(levels = 1:7, labels = c("Strongly\nDisagree", "Disagree", "Slightly\nDisagree", "Neither Agr\nnor Disagr", "Slightly\nAgree", "Agree", "Strongly\nAgree"))

d$lc_more_than_slightly_agree <- ifelse(d$comb_lc_score >= 6, "agree or strongly agree", "slightly or not agree") %>%
    factor(
      levels = c("slightly or not agree", "agree or strongly agree"),
      labels = c("slightly or not agree", "agree or strongly agree ('good range')")
    )

# check the coding
d %>%
  dplyr::filter(!is.na(d$lc_bin)) %>%
  group_by(
    lc_bin,
    lc_agree_disagree,
    lc_more_than_slightly_agree
  ) %>%
  summarise(
    n = n(),
    A_or_B = mean(A_or_B)
  )


d$race_cat <- ifelse(d$black, "black", ifelse(d$hispanic, "hispanic", ifelse(d$amindian, "amindian", ifelse(d$pacisl, "pacisl", ifelse(d$asian, "asian", ifelse(d$multirace, "multirace", ifelse(d$white, "white", NA))))))) 

d$race_grouped <- d$race_cat

race_levels <- c("black", "hispanic", "amindian", "pacisl", "asian", "multirace", "white")
race_labels <- c("Black or African-\nAmerican", "Latinx", "Native\nAmerican", "Pacific\nIslander", "Asian or\nAsian-American", "Multi-\nRace", "White or European-\nAmerican")

groups_reduced <- c("amindian", "multirace", "pacisl")
race_levels_reduced <- race_levels[!race_levels %in% groups_reduced]
race_labels_reduced <- race_labels[which(race_levels %in% race_levels_reduced)]

race_levels_intercept <- c("white", setdiff(race_levels, "white"))
race_labels_intercept <- c("White or European-\nAmerican", setdiff(race_labels, "White or European-\nAmerican"))

d$race_f <- factor(d$race_cat, levels = race_levels, labels = race_labels)
# this will set unused values to NA on purpose
d$race_reduced_f <- factor(d$race_cat, levels = race_levels_reduced, labels = race_labels_reduced) 
d$race_intercept_f <- factor(d$race_cat, levels = race_levels_intercept, labels = race_labels_intercept)

d$gender_f <- factor(d$gender, levels = c("Female", "Male or nonbinary"), labels = c("Female", "Male"))

COLORS <-  c("#155994", "#00B2EE")
SCALE_FILL <- scale_fill_manual(
        breaks = c("Negative conditions", "Positive conditions"),
        values = COLORS,
        name = "Learning conditions"
    ) 
SCALE_FILL_NOLAB <- scale_fill_manual(
        breaks = c("Negative conditions", "Positive conditions"),
        values = COLORS,
        name = ""
    ) 
THEME <- theme(
    legend.position = "bottom",
    axis.title.x = element_text(size = 14),
    panel.background = element_blank()
    ) 

lm(A_or_B ~ lc_agree_disagree * marginalized + q4_non_math_gpa, data = d, family = "binomial") %>%
    summary 

d$q4_non_math_gpa_bins <- floor(d$q4_non_math_gpa) %>%
  factor(., levels = c(0,1,2,3,4), labels = c("F's", "D's", "C's", "B's", "A's"))

d$q4_non_math_gpa_two_bins <- ifelse(d$q4_non_math_gpa <= 2, "below 2.0", ifelse(d$q4_non_math_gpa > 2, "above 2.0", NA)) %>%
  factor(., levels = c("below 2.0", "above 2.0"), labels = c("Other class GPA\nbelow 2.0", "Other class GPA\nabove 2.0"))

table(d$q4_non_math_gpa_two_bins) %>%
    xtable()

# check this coding
d %>%
  group_by(q4_non_math_gpa, q4_non_math_gpa_bins, q4_non_math_gpa_two_bins) %>%
  summarise(n = n())

dcc <- d[complete.cases(d),]
#cor.test(dcc$comb_lc_score, dcc$q4_math_grade) r(1124) = .10, p < .001


# overall grade points
ggplot(d, aes(lc_bin, q4_math_grade)) +
    geom_line(stat = "summary", fun.y = "mean") +
    ug.se_error_bar +
    coord_cartesian(ylim = c(1.5, 3.0)) +
    ylab("Numeric value of grade in math class") +
    xlab("Scale response value of average learning conditions score") +
    THEME

# overall likelihood of A/B as a function of all scale points
whole_scale_plot <- ggplot(d[!is.na(d$lc_bin),], aes(x = lc_bin, A_or_B)) +
    geom_line(stat = "summary", fun.y = "mean") +
    ug.se_error_bar +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    ylab("Likelihood of earning an A or a B in class") +
    xlab("Scale response value of average\nlearning conditions score") +
    THEME +
    theme(axis.text.y = element_text(size = 14))

ggsave(REPO %+% "graphs/all_scale_points.png", whole_scale_plot, width = 4, height = 3, dpi = "print")


# small race groups removed
d_reduced <- dplyr::filter(
      d,
      !is.na(race_reduced_f),
      !is.na(lc_agree_disagree)
    )

gender_plot <- ggplot(
    d[!is.na(d$lc_agree_disagree), ],
    aes(gender_f, A_or_B, fill = lc_agree_disagree)
    ) +
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge", color = "black") +
  coord_cartesian(ylim = c(0, .7)) +
  ug.se_error_bar +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  ylab("Likelihood of earning an\nA or a B in class") +
  xlab("") +
  SCALE_FILL +
  THEME

ggsave(REPO %+% "graphs/lc_by_race3.pdf", width = 7, height = 4, units = "in")


race_plot <- ggplot(
    d_reduced,
    aes(reorder(race_reduced_f, A_or_B), A_or_B, fill = lc_agree_disagree)
    ) +
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge", color = "black") +
  coord_cartesian(ylim = c(0, .7)) +
  ug.se_error_bar +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  ylab("Likelihood of earning an\nA or a B") +
  xlab("") +
  SCALE_FILL +
  THEME


# by non-math GPA
gpa_plot <- ggplot(
    d[!is.na(d$lc_agree_disagree),], 
    aes(q4_non_math_gpa_two_bins, A_or_B, fill = lc_agree_disagree)
  ) +
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge", color = "black") +
  ug.se_error_bar +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  coord_cartesian(ylim = c(0, .7)) +
  ylab("Likelihood of earning an A or a B in other classes") +
  xlab("\nOther Class GPA") +
  SCALE_FILL +
  THEME
ggsave(REPO %+% "graphs/lc_by_nonmath_gpa.pdf")

race_gpa_plot <- arrangeGrob(
  race_plot + theme(legend.position = "none"),
  gpa_plot + theme(legend.position = "right") + xlab("") + ylab(""),
  nrow = 1
)

race_gender_plot <- arrangeGrob(
  race_plot + theme(legend.position = "none"),
  gender_plot + theme(legend.position = "right") + xlab("") + ylab(""),
  nrow = 1
)

ggsave(REPO %+% "graphs/race_gpa.png", race_gpa_plot, width = 10, height = 3, units = "in", dpi = "print")
ggsave(REPO %+% "graphs/race_gender.png", race_gender_plot, width = 10, height = 3, units = "in", dpi = "print")
ggsave(REPO %+% "graphs/race_plot_external.png", race_plot, width = 5, height = 3, units = "in", dpi = "print")

# get the overall percentages
d %>%
    dplyr::filter(!is.na(lc_agree_disagree)) %>%
    group_by(lc_agree_disagree) %>%
    summarise(A_or_B = mean(A_or_B))

minimal_model <- glm(A_or_B ~ lc_agree_disagree, data = d, family = "binomial")
stargazer(minimal_model,
  star.cutoffs = c(.05, .01, .001),
  notes        = "1 star p<.05; 2 stars p<.01; 3 stars p<.001",
  notes.label  = "",
  notes.append = FALSE,
  single.row=TRUE,
  header=FALSE
  )

all_controls_glm <- glm(A_or_B ~ lc_agree_disagree + q4_non_math_gpa + race_intercept_f + ell + frpl + school,
                    data = d, family = "binomial") 
stargazer(all_controls_glm,
  star.cutoffs = c(.05, .01, .001),
  notes        = "1 star p<.05; 2 stars p<.01; 3 stars p<.001",
  notes.label  = "",
  notes.append = FALSE,
  single.row=TRUE,
  header=FALSE
)

all_controls_lm <- lm(A_or_B ~ lc_agree_disagree + q4_non_math_gpa + race_intercept_f + ell + frpl + school,
                    data = d, family = "binomial") 
summary(all_controls_lm)


d %>%
    group_by(race_cat, gender) %>%
    summarise(n = n())

d_AA_boys <- d %>%
    dplyr::filter(
        race_cat %in% "black",
        !gender %in% "Female"
    )

d_AA_boys %>%
    group_by(lc_agree_disagree) %>%
    summarise(
        n = n(),
        A_or_B = mean(A_or_B)
    )


glm(A_or_B ~ lc_agree_disagree + q4_non_math_gpa + ell + frpl, data = d_AA_boys, family = "binomial") %>%
    summary # not quite significant

cor.test(d_AA_boys$lc_agree_disagree_numeric, d_AA_boys$A_or_B)

```

```[r]



## discipline
ggplot(d, aes(as.factor(lc_bin), q4_suspensions)) +
  geom_boxplot() 

ggplot(d[!is.na(d$lc_bin),], aes(as.factor(lc_bin), as.numeric(q4_suspensions_any))) +
  geom_bar(stat = "summary", fun.y = mean) +
  ug.se_error_bar

ggplot(d[!is.na(d$lc_bin),], aes(as.factor(lc_bin), as.numeric(q4_suspensions))) +
  geom_bar(stat = "summary", fun.y = mean) +
  ug.se_error_bar 

## absences
ggplot(d, aes(as.factor(lc_bin), q4_suspensions)) +
  geom_boxplot() 

ggplot(d[!is.na(d$lc_bin),], aes(as.factor(lc_bin), as.numeric(q4_present_high))) +
  geom_bar(stat = "summary", fun.y = mean) +
  ug.se_error_bar
```


```{r}
# item analyses
# Do particular LCs matter for particular groups of students?

dm <- d[c("student_id", "race_cat", "lc_bin", "tc", "fg", "mw", "A_or_B")] %>%
  melt(id.vars = c("student_id", "race_cat", "A_or_B"), measure.vars = c("tc", "fg", "mw")) %>%
  rename(lc_score = value) %>%
  mutate(lc_score_bins = floor(lc_score))

dm$lc_agree_disagree <- ifelse(dm$lc_score > 5, "agree or strongly agree", "Negative conditions") %>%
    factor(levels = c("Negative conditions", "agree or strongly agree"))

# overall lines
ggplot(dm, aes(x = lc_score_bins, y = A_or_B, fill = race_cat)) +
  geom_line(stat = "summary", fun.y = mean) +
  ug.se_error_bar +
  facet_grid(variable ~ .)

A_or_B_by_race <- ggplot(dm[!is.na(dm$lc_agree_disagree),], aes(x = race_cat, y = A_or_B, fill = lc_agree_disagree)) +
  geom_bar(stat = "summary", fun.y = mean, position = "dodge") +
  ug.se_error_bar  +
  facet_grid(variable ~ .) + 
  ylab("Likelihood of earning an A or a B") +
  xlab("Race") +
  SCALE_FILL + 
  THEME

ggsave(REPO %+%  "graphs/AorB_by_race.png", A_or_B_by_race, width = 10, height = 7, units = "in", dpi = "print")


### plotting comb_lc by race

lc_by_race <- ggplot(dm, aes(race_cat, lc_score)) +
  geom_bar(stat = "summary", fun.y = "mean") +
  ug.se_error_bar +
  facet_grid(variable ~ .) + 
  xlab("Race") + 
  ylab("LC scores") +
  SCALE_FILL + 
  THEME

  ggsave(REPO %+% "graphs/lc_by_race.png", lc_by_race, width = 10, height = 7, units = "in", dpi = "print")



```

# Tweet storm 2020
```{r}
# When teachers create supportive learning conditions, students of color are 68% more likely to earn As and Bs
d$race_disadv <- ifelse(
  d$race_cat %in% c("hispanic", "black", "pacisl", "multirace", "amindian"), "Str. Disadv.",
  ifelse(d$race_cat %in% c("white", "asian"), "Str. Adv.", NA)
)

```