---
title: "DESCRIPTIVE TITLE"
author: "NAMES OF CONTRIBUTING ANALYST(S)"
date: "MONTH/YEAR (USUALLY)"
output: 
  html_document:
    fig_caption: no
    toc: yes
    theme: spacelab
    css: ~/Sites/gymnast/Rmd/RMD_styles.css
---

# Introduction

[DESCRIBE THE PURPOSE AND CONTENT OF THIS DOCUMENT]

## Input Files

[LIST AND DESCRIBE ALL FILES THAT ARE READ INTO THIS SCRIPT]

## Output Files

[LIST AND DESCRIBE ALL FILES THAT ARE WRITTEN FROM THIS SCRIPT]


# Setting the environment

## Set User Inputs
[SET USER INPUT VARIABLES BELOW; USER INPUT VARIABLES ARE
INFORMATION THAT NEEDS TO BE SET BY THE ANALYST; E.G., 
OPTIONS TO EVALUATE PARTICULAR CHUNKS, ANY SCRIPT-LEVEL 
CONDITIONAL LOGIC, ETC.CONSTANTS SHOULD BE IN ALL CAPS]

```{r results='asis'}

```


## Load libraries

```{r results='asis', message=FALSE, warning=FALSE}
# source gymnast functions
tryCatch({
    source("~/Sites/gymnast/R/util.R", chdir = TRUE)
    source("~/Sites/gymnast/R/util_qualtrics_cleaning.R", chdir = TRUE)
    source("~/Sites/gymnast/R/util_graphing.R", chdir = TRUE)
}, error = function(e){
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_legacy.R")
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_qualtrics_cleaning.R")
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_graphing.R")
})

# source any additional packages that are NOT loaded in gymnast
# note that almost any package we would ever use is always in gymnast

# set stringsAsFactors to FALSE, and add any other global R settings
options(stringsAsFactors = FALSE)

# set results to 'asis' for all chunks
# (can also add any global rmarkdown settings here)
opts_chunk$set(results = 'asis')
```

## Local helper functions

[PUT ALL YOUR LOCALLY-CREATED HELPER FUNCTIONS HERE. MAKE SURE TO 
 CONTRIBUTE ANY GOOD ONES TO the [Miscellaneous Code Archive](https://docs.google.com/document/d/10_K8clWHUQIbO5BWXViiZBXMbRDkni7ypuBJ54l_KWE/edit) 
 BY CREATING A [gist](https://gist.github.com/).]


```{r}

# lh.helper_function <- function()

```

# Data Preparation

[THIS IS A GOOD PLACE TO LIST ASSUMPTIONS ABOUT THE STRUCTURE OF THE INCOMING DATA]

## Load data

```{r}

# source salt file--note that a salt is a password, and thus should NEVER be printed
# directly to the console or to the html output!!!! It should only be sourced directly 
# from a crypt folder.

# salt <- source("salt.R")

data_files_to_load <- list(
    "br_1" = "baseline_records_1.csv",
    "cr_1" = "course_records_1.csv"
)

key_files_to_load <- list(
    "ck" = "column_key.csv",
    "tdk" = "term_dates_key.csv",
    "lgk" = "letter_grade_key.csv",
    "v1k" = "variable1_key.csv", # e.g., race-recode values
    "v2k" = "variable2_key.csv"
)

# raw_file_paths <- util.find_crypt_paths(files_to_load)

# d_raw is a list of data.frames corresponding to the .csvs in `files_to_load`
# d_raw <- util.read_csv_files(raw_file_paths) 



```

## Pre-process datasets

[USE THIS SECTION FOR CLEANING OPERATIONS INVOLVING INDIVIDUAL DATA FRAMES]

### De-identify

```{r}

# source the salt
# source(util.find_crypt_paths(list(salt = "salt.R"))$salt)

# loop through d_raw and:
# - Hash all id variables with the salt
# - Remove all non-whitelisted variables with uniqueness above a certain threshold

# d_di is a list of de-identified data.frames

# here you can save a hash/id table in the crypt folder, too. This can be useful 
# for error checking.

```

### Clean columns

#### Standardize column names

```{r}
# d_rn is a list of renamed data.frames

```

#### Standardize column values

* any variable recoding (ideally using a key file)
* includes grade recoding with `glk` if applicable

```{r}
# d_rc  is a renamed, recoded data.frames (or list of data.frames)
# this convention works well in the absence of key files:

# key <- list(old_values = c(1,2,3), new_values = c("a", "b", "c"))
# d_rc$var <- util.recode(d_rc$var, key$old_values, key$new_values)
```

### Clean rows

#### Logic for handling rows with missing data


#### Logic for handling duplicated index values

```{r}

# d_dh is a data.frame with duplicates handled (or list of data.frames)

# Frequently used procedure for handling duplicates in survey data
# 1. Remove all rows where time on task < 2 minutes
# 2. Identify subject_ids that are still duplicated
# 3. Remove all records corresponding to the still-duplicated IDs

```

### Perform key merges

A key merge is any merge that merges a key file with a 
data.frame without changing its type; e.g., merging a stem_key into a 
course_records data.frame.

### Conduct checks on the pre-processed data

#### Unique indexes
Make sure your indexes are unique (could use [check_index_is_unique](https://gist.github.com/sarahgripshover/3192e2ce1128bb5e79fc3edc2471d9eb)).

#### Expected numbers of rows

This check is especially important if you've done key merges

### Optionally, save de-identified, pre-processed data

[YOU MAY WISH TO CREATE A SAVED VERSION OF YOUR DE-IDENTIFIED, PRE-PROCESSED 
DATA FILES, ESPECIALLY IF PRE-PROCESSING IS SLOW. IF SO, DO SO HERE.]

```{r}

```