---
title: "DESCRIPTIVE TITLE"
author: "NAMES OF CONTRIBUTING ANALYST(S)"
date: "MONTH/YEAR (USUALLY)"
output: 
  html_document:
    fig_caption: no
    toc: yes
    theme: spacelab
    css: ~/Sites/gymnast/Rmd/RMD_styles.css
---

# Introduction

[DESCRIBE THE PURPOSE AND CONTENT OF THIS DOCUMENT]

## Input Files

[LIST AND DESCRIBE ALL FILES THAT ARE READ INTO THIS SCRIPT]

## Output Files

[LIST AND DESCRIBE ALL FILES THAT ARE WRITTEN FROM THIS SCRIPT]


# Setting the environment

## Set User Inputs
[SET USER INPUT VARIABLES BELOW; USER INPUT VARIABLES ARE
INFORMATION THAT NEEDS TO BE SET BY THE ANALYST; E.G., 
OPTIONS TO EVALUATE PARTICULAR CHUNKS, ANY SCRIPT-LEVEL 
CONDITIONAL LOGIC, ETC.CONSTANTS SHOULD BE IN ALL CAPS]

```{r results='asis'}

```


## Load libraries

```{r results='asis', message=FALSE, warning=FALSE}
# source gymnast functions
tryCatch({
    source("~/Sites/gymnast/R/util.R", chdir = TRUE)
    source("~/Sites/gymnast/R/util_qualtrics_cleaning.R", chdir = TRUE)
    source("~/Sites/gymnast/R/util_graphing.R", chdir = TRUE)
}, error = function(e){
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_legacy.R")
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_qualtrics_cleaning.R")
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_graphing.R")
})

# source any additional packages that are NOT loaded in gymnast
# note that almost any package we would ever use is always in gymnast

# set stringsAsFactors to FALSE, and add any other global R settings
options(stringsAsFactors = FALSE)

# set results to 'asis' for all chunks
# (can also add any global rmarkdown settings here)
opts_chunk$set(results = 'asis')
```

## Local helper functions

[PUT ALL YOUR LOCALLY-CREATED HELPER FUNCTIONS HERE. MAKE SURE TO 
 CONTRIBUTE ANY GOOD ONES TO the [Miscellaneous Code Archive](https://docs.google.com/document/d/10_K8clWHUQIbO5BWXViiZBXMbRDkni7ypuBJ54l_KWE/edit) 
 BY CREATING A [gist](https://gist.github.com/).]


```{r}

# lh.helper_function <- function()

```
    
    
# Merge data
    
In this section, you will merge data of different kinds; e.g., rbinding 
pre-processed data or merging datasets of different types (e.g., merging 
demographic info from baseline_records.csv with course_records.csv).


## Rbind like datasets

```{r}
# use util.rbind_union
```



## Aggregate and cast data


### Define relative time variable on time-dependent outcomes


### Create aggregated outcomes (by term, year, etc.)


## Merge unlike datasets


### Compute variables on merged data

[THESE ARE VARIABLES THAT ]

#### Create psychometric scales

[WE COMPUTE SCALES ON THE FULLY MERGED DATA BECAUSE WE USUALLY WANT 
 Z-SCORES CENTERED ON THE WHOLE SAMPLE, NOT WITHIN INDIVIDUAL SCHOOLS 
 OR DATASETS]
