---
title: "DESCRIPTIVE TITLE"
author: "NAMES OF CONTRIBUTING ANALYST(S)"
date: "MONTH/YEAR (USUALLY)"
output: 
  html_document:
    fig_caption: no
    toc: yes
    theme: spacelab
    css: ~/Sites/gymnast/Rmd/RMD_styles.css
---

# Introduction

[DESCRIBE THE PURPOSE AND CONTENT OF THIS DOCUMENT]

## Input Files

[LIST AND DESCRIBE ALL FILES THAT ARE READ INTO THIS SCRIPT]

## Output Files

[LIST AND DESCRIBE ALL FILES THAT ARE WRITTEN FROM THIS SCRIPT]


# Setting the environment

## Set User Inputs
[SET USER INPUT VARIABLES BELOW; USER INPUT VARIABLES ARE
INFORMATION THAT NEEDS TO BE SET BY THE ANALYST; E.G., 
OPTIONS TO EVALUATE PARTICULAR CHUNKS, ANY SCRIPT-LEVEL 
CONDITIONAL LOGIC, ETC.CONSTANTS SHOULD BE IN ALL CAPS]

```{r results='asis'}
# do you want to print code? TRUE will print the code in the html 
# output, FALSE will hide it.
PRINT_CODE <- TRUE
```


## Load libraries

```{r results='asis', message=FALSE, warning=FALSE}
# source gymnast functions
tryCatch({
    source("~/Sites/gymnast/R/util.R", chdir = TRUE)
    source("~/Sites/gymnast/R/util_qualtrics_cleaning.R", chdir = TRUE)
    source("~/Sites/gymnast/R/util_graphing.R", chdir = TRUE)
}, error = function(e){
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_legacy.R")
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_qualtrics_cleaning.R")
    source("https://raw.githubusercontent.com/PERTS/gymnast/master/R/util_graphing.R")
})

# source any additional packages that are NOT loaded in gymnast
# note that almost any package we would ever use is always in gymnast

# set stringsAsFactors to FALSE, and add any other global R settings
options(stringsAsFactors = FALSE)

# set results to 'asis' for all chunks
# (can also add any global rmarkdown settings here)
opts_chunk$set(results = 'asis')

# if the user wants a clean report with no code printed (as indicated 
# by the Boolean user input variable `PRINT_CODE`), set echo to FALSE.
# Also disable warnings and messages.
if(!PRINT_CODE){
    opts_chunk$set(echo = FALSE)
    opts_chunk$set(message = FALSE)
    opts_chunk$set(warning = FALSE)
}

```

## Local helper functions

[PUT ALL YOUR LOCALLY-CREATED HELPER FUNCTIONS HERE. MAKE SURE TO 
 CONTRIBUTE ANY GOOD ONES TO the [Miscellaneous Code Archive](https://docs.google.com/document/d/10_K8clWHUQIbO5BWXViiZBXMbRDkni7ypuBJ54l_KWE/edit) 
 BY CREATING A [gist](https://gist.github.com/).]


```{r}

# lh.helper_function <- function()

```

# Purpose

The purpose of the study was to improve the equity of learning outcomes 
among students [AT/IN] [COLLABORATING INSTITUTION/POPULATION/ETC.]. 

Specifically, we sought to improve community college students' likelihood 
of earning a passing grade in college-level math classes.


# Executive Summary

[THE EXECUTIVE SUMMARY SHOULD CONTAIN THE FOLLOWING INFORMATION]

* Practical importance—say why this problem is important to people
* Scientific "lead-up"—science (growth mindset, belonging, etc.) can help the problem
* Purpose of study w/language from our mission statement
* Results summary. Make sure to add a simple statement of the main result in *bold*.

[HERE IS AN EXAMPLE:]

[PRACTICAL IMPORTANCE] For millions of Americans, 
community college serves as an entry 
point for higher education, and the economic prosperity and social 
mobility that comes with it. Yet only 41% of students who begin 
community college manage to attain a certificate, earn a degree, 
or transfer to a four-year institution within six years.

[SCIENTIFIC LEAD-UP] There are many factors that 
affect students' achievement. Structural 
factors such as poverty play a role, as do students' previous 
academic preparation, the quality of teaching they receive in 
college, and the responsibilities students have to their 
families and jobs outside of school. Recent research has 
suggested that one important factor impacting studnets' 
achievement is their beliefs and feelings about school 
and about themselves, or their _learning 
mindsets_.

One important learning mindset concerns students' beliefs about 
intelligence. People sometimes think of intelligence as being like eye 
color---something fixed about you that can’t really be changed. 
We call this belief a “fixed mindset.” Research shows that 
when students think in a fixed mindset, they 
tend to have lower engagement with learning, less adaptive 
responses to academic setbacks, and eventually, 
worse academic outcomes. After all, if our basic 
intelligence can’t really be changed, what’s the point of 
working hard in a subject that doesn’t come naturally?

The opposite of a fixed mindset is called a growth mindset.
A growth mindset means understanding that intelligence is more like
muscle strength---you can increase it through effort, good study 
strategies, and seeking out challenges. When students think in
a growth mindset, they tend to be more motivated
and engaged learners, and they tend to do better academically
over time as well. They are more likely to stay resilient in the 
face of setbacks and put more effort into their school 
work, because they know it will pay off, even in subjects 
that may not come naturally at first. 

[PURPOSE OF STUDY WITH LANGUAGE FROM MISSIONS STATEMENT]

Fortunately, it is possible to change our mindsets about 
intelligence! A number of studies have found students can learn to
adopt a growth mindset through brief, 
online activities that require only an hour---or even less---of
students’ time, and that acquiring a growth mindset can
improve students’ academic performance. 

The aim of the 
study was to do exactly that: [COLLABORATING INSTITUTION] and 
PERTS have delivered an online activity to students 
in developmental math classes and skills classes designed
to teach them to think with a growth mindset. This shift in 
thinking is expected to increase their likelihood passing 
difficult coursework, especially in challenging subjects such 
as math and science. Eventually, these gains in academic performance 
may translate to improvements in overall student persistence, 
degree attainment, and transfer rates to four-year colleges. 

Thus, aimed to promote equity at [PARTNER 
INSTITUTION] by teaching students in developmental math and skills 
classes--students who often face the greatest academic challenges 
and are most vulnerable to negative messages about intelligence--
to think in a growth mindset.

[BRIEF STATEMENT ABOUT RESULTS] Preliminary results from this 
study indicate that the program was successful. Students who 
completed the growth mindset activity were **11% more likely to 
earn credit in math courses.** Earning math credits is 
important because required math classes often funcion as "gatekeeper 
courses," holding students back from further progress if they are not 
able to earn a passing grade.


# Description of the Program

## Program overview

[THIS IS A NARRATIVE SUMMARY OF THE EXPERIMENT; ESSENTIALLY, THE 
METHODS SECTION. SHOULD INCLUDE THE FOLLOWING INFORMATION]

* What did students do as part of the program?
* How did instructors implment the program?
* How many instructors implemented the program?
* When did they complete the program?
* How many students completed it?
* What are some examples of things students wrote?

[EXAMPLE]
To participate in the College Perspectives Program, students completed an 
online activity designed to teach them to think in a growth mindset 
by expert researchers at Stanford University 
including Carol Dweck and Greg Walton. The program was delivered 
online. Students clicked on a link which took them to a website
where they were shown evidence that the brain can change and become 
smarter. They learned how neural plasticity continues into adulthood, 
and that people of any age can become substantially smarter with hard 
work, help from others, and good study strategies. Students then 
wrote a brief letter to help these other students think in a growth mindset.
Importantly, the exercise did NOT tell students they should have a 
growth mindset. It is very important not to do this. When students are 
told to have a growth mindset, it can make them feel defensive and 
override the helpfulness of the message. 

They completed the activity as a homework assignment, and it 
took them about 20 minutes.



## In students' own words

```{r}

# STUDENT_QUOTES <- quotes[quotes$school_name %in% SCHOOL_NAME, "quote"]
# 
# for(quote in STUDENT_QUOTES){
#     cat('<blockquote><i>')
#     cat('"')
#     cat(quote)
#     cat('"')
#     cat('</i></blockquote>')
# }

```

# Results

## Demographics/psychometrics summary

## Effect of treatment

## Moderation



# Conclusions and next steps

[SAY WHAT WE CAN CONCLUDE FROM THESE RESULTS, AND WHAT THE NEXT STEPS 
 ARE FOR THE RESEARCH COLLABORATION]

[EXAMPLE]

The results from this study are extremely promising. A brief program 
that students completed in 20 minutes as a homework assignment improved 
their rate of passing math classes by 11%. [COLLABORATING INSTITUTION] 
is invited to continue using the growth mindset activity, for free, 
as long as these positive effects continue.


# About PERTS

PERTS is an organization that empowers educators 
to improve student outcomes by applying research-based practices.
Education research has a serious problem when it comes to 
translating ideas into practices. Concepts that are often 
untested at scale become fads that educators are required to 
implement in their classrooms without proper training, and 
students end up suffering the consequences. Promising 
research is left in the dust when the “Next Big Thing” 
comes along and policy makers repeat the cycle.

Our mission at PERTS is to improve the equity of 
learning outcomes by bridging the gap between cutting-edge 
research and implementation practices. We believe that 
properly scaling educational research can empower schools 
to reduce inequity and create better experiences for students 
and teachers. Learn more at (www.perts.net)[www.perts.net].


# Acknowledgements

[SHOUT-OUTS FOR RELEVANT STAKEHOLDERS GO HERE]

We extend a heartfelt thank-you to the students, faculty, and 
administrators at [COLLABORATING INSTITUTION]. We especially thank 
[COORDINATOR(S)] for [HIS/HER] outstanding effort to make 
the program a success.

## Appendix: Methodological and technical details

### Note on interpreting statistics

(e.g., “we used something called regression analysis to examine the impact of the treatment”)

### Experiment design, procedure & methodology details 

### Scale alphas

### Power Analysis

### Extra Tables

### Extra Figures