---
title: "EP analysis 17-18.Rmd"
author: "Daniel Greene"
date: '`r format(Sys.time(), "%B %d, %Y")`'
output:
  pdf_document:
    fig_width: 9
    fig_height: 7
    fig_caption: yes
  html_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 9
    toc_depth: 2  
---

# Summary

This document analyzes relationships between student learning conditions (LCs) and engagement for the Engagement Project in the 2017-2018 school year. It is primarily intended to test hypotheses for replication in the 2018-2019 dataset.

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

############### USER-DEFINED INPUTS #####################################

general_data_folder_crypt_path <- "old 2017-2018 EP data"
input_data_crypt_path <- "Data for 2018-2019 EP analysis/old 2017-2018 EP data/3 - EP 2017-2018 clean data ready for analysis.csv"

```

```{r, results='hide', echo=FALSE}

############### LOAD LIBRARIES AND PATHS #####################################

options(stringsAsFactors = FALSE)
options(xtable.comment = FALSE)
github_base_path <- "https://raw.githubusercontent.com/PERTS/gymnast/master/"

tryCatch({
    source("~/Sites/gymnast/R/util.R")
    gymnast_install()
    library(tidyverse)
    source("~/Sites/gymnast/R/util_data_summaries.R")
    source("~/Sites/gymnast/R/util_qualtrics_cleaning.R")
    source("~/Sites/gymnast/R/util_graphing.R")
    source("~/Sites/gymnast/R/util_scale_computation.R")
    source("~/Sites/gymnast/R/util_dfc.R")
}, error = function(e){
    source(github_base_path %+% "R/util.R")
    gymnast_install()
    source(github_base_path %+% "R/util_data_summaries.R")
    source(github_base_path %+% "R/util_qualtrics_cleaning.R")
    source(github_base_path %+% "R/util_graphing.R")
    source(github_base_path %+% "R/util_scale_computation.R")
    source(github_base_path %+% "R/util_dfc.R")
})

library(tidyverse)
library(lubridate)
library(kableExtra)
library(scales)
library(corrplot)


# Set "today" - by default, use the real today
TODAY <- lubridate::ymd(Sys.Date())

```

```{r, echo=FALSE}

############### LOAD DATA #####################################

d <- util.find_crypt_paths(list(a = input_data_crypt_path))$a %>%
  read.csv()

# Final factor-setting
d$race <- relevel(factor(d$race), ref = "White & Asian")
d$gender <- relevel(factor(d$gender), ref = "Female")

# Create first-to-last df for H2
# And drop all rows where survey_ordinal_ftl == 0, because they are students with just one observation
d_ftl <- d %>%
  arrange(student_id, survey_ordinal) %>%
  group_by(student_id) %>%
  summarise(survey_ordinal_ftl = last(survey_ordinal) - first(survey_ordinal),
            effort_ftl = last(effort) - first(effort),
            comb_lc_score_ftl = last(comb_lc_score) - first(comb_lc_score),
            first_comb_lc_score = first(first_comb_lc_score),
            gender = first(gender),
            race = first(race),
            prior_gpa = first(prior_gpa),
            class_id = first(class_id),
            teacher_id = first(teacher_id),
            team_id = first(team_id)) %>%
  filter(survey_ordinal_ftl > 0)


# ds.summarize_by_column(d)


```

# Correlation table

```{r, fig.height=5}

correlation_vars <- c("comb_lc_score", "effort", "expected_grade",
                      "prior_gpa", "comb_lc_score_classmates")

cor( d[, correlation_vars], use="pairwise" ) %>% 
    corrplot( type="lower", method = "number", tl.col = "black")

```


# H1a: Combined LC score predicts self-reported effort.

```{r}

summary(lmer(effort ~ comb_lc_score + gender + race + prior_gpa + 
               ( 1 | student_id ) + ( 1 | class_id ) + ( 1 | teacher_id ) + ( 1 | team_id ),
             data = d))

```

H1a confirmed: Combined LC score does predict concurrent self-reported effort, even controlling for gender and race. The LMER model ran normally.

# H1b: Combined LC score predicts self-reported expected grade.

```{r}

summary(lmer(expected_grade ~ comb_lc_score + gender + race + prior_gpa +
               ( 1 | student_id ) + ( 1 | class_id ) + ( 1 | teacher_id ) + ( 1 | team_id ),
             data = d))

```

H1b confirmed: Combined LC score does predict concurrent self-reported expected grade. The full LMER model ran normally.


# H2: First-to-last-observation changes in students’ LCs predict corresponding changes in effort.

```{r}

# Using FTL model:
# Model failed to converge with max|grad| = 0.0183099 (tol = 0.002, component 1)
# summary(lmer(effort_ftl ~ comb_lc_score_ftl + first_comb_lc_score +
#                gender + race + prior_gpa +
#                ( 1 | class_id ) + ( 1 | teacher_id ) + ( 1 | team_id ),
#              data = d_ftl))

# Model runs after removing class_id
summary(lmer(effort_ftl ~ comb_lc_score_ftl + first_comb_lc_score +
               gender + race + prior_gpa +
               ( 1 | teacher_id ) + ( 1 | team_id ),
             data = d_ftl))


```

H2 confirmed with a simpler model obtained after removing class-id random effect to achieve model convergence (probably because class and teacher overlap a lot). Changes in combined LC score predict corresponding changes in self-reported effort, even after controlling for first LC score, survey ordinal, and prior GPA.

# H3: Students’ personal perceptions of LCs are correlated with the LCs of their classmates.

```{r}

summary(lmer(comb_lc_score ~ comb_lc_score_classmates + gender + race + prior_gpa +
               ( 1 | student_id )  + ( 1 | class_id ) + ( 1 | teacher_id ) + ( 1 | team_id ),
             data = d))

```

H3 confirmed: Combined LC score is strongly predicted by the average combined LC score of one's classmates. The full LMER model ran normally.

