---
title: "Power Analysis for EP 2018-19"
author: "Sarah Gripshover"
date: "August 2018"
output: 
    html_document:
        fig_caption: no
        toc: yes
        theme: spacelab
        css: ~/Sites/gymnast/Rmd/rmd_styles.css
---


# Introduction


# Course-level outcomes

We will likely have course-level data from EOS (50 classes), Relay (50 classes), NTC (15-30 classes), and Summit (5 classes), so conservatively 100 classes in total. We’re maybe going to collect data from a district or two as well. What effect sizes can we detect with these data?

## Student-level analyses

Our first set of analyses will estimate effects at the student level (i.e., how well students' experience of learning conditions map on to students' outcomes). The models assume shared variance within-classrooms.

```{r message=FALSE, warning=FALSE, results='asis'}
library(MASS)
library("dplyr")
library("xtable")
source("~/Sites/gymnast/R/util.R")
library("tidyr")

# set parameters

# user parameters
model_formula <- "outcome_re ~ mean_LC + survey_grades"
prob_threshold <- .05
n_sims <- 100
Vclass <- 1 # value for shared variance within classroom

# properties of data

# numbers
n_classes <- 100
n_students_per_class <- 25

# variable names & properties (mus and sds must appear in same order as var_names)
var_names <- c("survey_grades", "mean_LC", "outcome")
mus <- c(4, 4, 4)
sds <- c(2, .1, 2)

# r values
r_survey_grades_outcome <- .5
r_mean_LC_outcome <- .25 # this is the effect size we're testing
r_mean_LC_survey_grades <- .4 # 

####################################################################################

# create a correlation matrix based on r values
generate_cor_mat <- function(r_mean_LC_outcome, r_mean_LC_survey_grades, r_survey_grades_outcome){
    cor_mat <- matrix(
        c(1, r_mean_LC_survey_grades, r_survey_grades_outcome,
          r_mean_LC_survey_grades, 1, r_mean_LC_outcome,
          r_survey_grades_outcome, r_mean_LC_outcome, 1),
        nrow = 3, ncol = 3
    )
    return(cor_mat)
}


generate_data <- function(mus, sds, n_students_per_class, n_classes, cor_mat, var_names, Vclass){
    # generates & returns data.frame with specified parameters
    
    # create the correlated data
    
    # number of cases
    n_rows <- n_students_per_class * n_classes
    # Get a covariance matrix from corr mat by multiplying by the product of the two standard deviations vectors.
    sd_prods <- sds %*% t(sds)
    cov_mat <- cor_mat * sd_prods
    df <- mvrnorm(n = n_rows, mu = mus, Sigma = cov_mat) %>%
        as.data.frame
    names(df) <- var_names
    
    # now add error variance for classes (and maybe, students)
    df$student_id <- 1:n_rows
    df$class_id <- rep(1:n_classes, each = n_students_per_class)
    
    class_re <- rnorm(n_classes, 0, sqrt(Vclass))
    df$class_re <- class_re[df$class_id]
    df$outcome_re <- df$outcome + df$class_re
    
    # double-check the correlation structure
    # if(!all(round(cor(df[var_names]), 2) == cor_mat)){
    #     util.warn("Generated data correlation matrix does not match cor_mat input")
    # }
    
    # still need to adjust the variances to match sds
    
    return(df)
}

model_data <- function(df, model_formula){
    model <- lm(model_formula, data = df)
    return(model)
}

run_sims <- function(n_sims, mus, sds, n_students_per_class, n_classes, cor_mat, var_names, Vclass){
    # generates & analyzes fake data with specified parameters, returns a list of models
    models <- list()
    for(i in 1:n_sims){
        df <- generate_data(mus, sds, n_students_per_class, n_classes, cor_mat, var_names, Vclass)
        model <- model_data(df, model_formula)
        models[[i]] <- model
    }
    return(models)
}

summarise_power <- function(models, prob_threshold){
    
    probs <- lapply(models, function(model) return(coef(summary(model))[2, 4])) %>% unlist
    betas <- lapply(models, function(model) return(coef(summary(model))[2, 1])) %>% unlist
    
    power_summary <- data.frame(
        prob = probs,
        beta = betas
    ) %>%
        mutate(
            is_pos_hit = beta > 0 & prob <= prob_threshold,
            is_pos_miss = beta > 0 & prob > prob_threshold,
            is_neg_hit = beta < 0 & prob <= prob_threshold,
            is_neg_miss = beta < 0 & prob > prob_threshold,
            prob_10 = prob <= .1,
            prob_05 = prob <= .05,
            prob_cat = ifelse(prob_05, ".05", ifelse(prob_10, ".10", "ns"))
        )
    
    return(power_summary)
}

cor_mat <- generate_cor_mat(r_mean_LC_outcome, r_mean_LC_survey_grades, r_survey_grades_outcome)
models <- run_sims(n_sims, mus, sds, n_students_per_class, n_classes, cor_mat, var_names, Vclass)
power_summary <- summarise_power(models, prob_threshold)

ggplot(power_summary, aes(x = beta, color = prob_cat, fill = prob_cat)) +
    geom_histogram() +
    geom_vline(xintercept = 0)


```

Now run sims for different values of r to figure out what the minimum effect is that can be detected with the proposed sample characteristics, modeling technique, etc. Note that for different values of the non-main-effect correlations in our framework (i.e., for values of `r_survey_grades_outcome` and `r_mean_LC_survey_grades`), our main-effect correlation (`r_mean_LC_outcome`) becomes vulnerable to suppression effects below a certain value.

In addition to our power threshold, we want to know where that "inflection point" is, where the majority of beta values start being negative and increasingly statistically significant. 

```{r}
# r values
rs_survey_grades_outcome <- seq(.2, .9, by = .1) # we actually know more or less what these values are.
rs_mean_LC_survey_grades <- seq(0, .9, by = .1)
rs_mean_LC_outcome <- seq(.15, .3, by = .01)

power_threshold <- .8 # this is the desired statistical power

# other params
n_sims <- 20

# create a cartesian product of all the r-vectors above
non_effect_corrs_df <- expand.grid(
    rs_survey_grades_outcome,
    rs_mean_LC_survey_grades
) %>%
    setNames(c("survey_grades_outcome", "mean_LC_survey_grades"))

# for each possible combination of non-effect-r's:
for(row in 1:nrow(non_effect_corrs_df)){
    
    # for all the effect_size values being tested, compute the proportion positive and negative hits 
    # line them up in an object like r_summary (unmelted), and find the first row where neg_hit_props == 0 and
    # pos_hit_props >= power_threshold. This is the minimum detectable effect.
    # save the minimum detectable effect in the non_effect_corrs_df (minimum_effect column)
    # also save the inflection point; i.e., the highest effect-size r at which we start to see suppression (max_suppression column)
    
    # so we'll have a data.frame with the same number of rows as non_effect_corrs_df, and two additional columns:
    # one for the min detectable effect, and one for the highest effect r-value where some of the models showed significant suppression.
}

# then I'll want some way of graphing the relation of both non-effect r-values to the min detectable effect and max suppression values.
# maybe super-imposed line graphs?




get_power_summaries <- function(cor_mat, n_sims, mus, sds, n_students_per_class, n_classes, var_names, Vclass){
    power_summaries <- list()
}

rcov <- r_mean_LC_survey_grades
for(r in rs_mean_LC){
    cor_mat <- generate_cor_mat(r_mean_LC_outcome = r, r_mean_LC_survey_grades = rcov, r_survey_grades_outcome)
    models <- run_sims(n_sims, mus, sds, n_students_per_class, n_classes, cor_mat, var_names, Vclass)
    power_summary <- summarise_power(models, prob_threshold)
    # what is the proportion of positive hits and negative hits?
    power_summaries[[which(rs_mean_LC == r)]] <- power_summary
}

# count all the positive/negative hits
pos_hit_props <- lapply(power_summaries, function(df) sum(df$is_pos_hit)/nrow(df)) %>% unlist
neg_hit_props <- lapply(power_summaries, function(df) sum(df$is_neg_hit)/nrow(df)) %>% unlist

r_summary <- data.frame(effect_size = rs_mean_LC_outcome, pos_hit_props = pos_hit_props, neg_hit_props = neg_hit_props) %>%
    melt(id.vars = "effect_size") %>%
    mutate(direction = gsub("_hit_props", "", variable)) %>%
    rename(proportion_hits = value)
r_summary

ggplot(r_summary, aes(effect_size, proportion_hits, color = direction)) +
    geom_line() +
    geom_point()

```



# Date-linked outcomes