---
# output: 
#   html_document:
#     fig_caption: no
#     toc: no
#     theme: spacelab
#     css: rmd_styles.css
title: "Creating EP 2018-2019 test data"
author: "Daniel Greene"
date: "August 11, 2018"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    fig_width: 9
    fig_height: 7
    fig_caption: yes
---


# Introduction

This script is for transforming test data for the EP 2018-2019 pilot. The test data was originally created using Qualtrics' tool for creating test responses, as described here:
https://docs.google.com/document/d/1FqwfjLKLcJJknfE8AZcy6aVHiJjiuzqpRz1QsfTNE_Y/edit#

What aspects of the data need to be fixed here?
- Participant_id and token are currently fixed test values and need to be changed or randomized to match new and old participants as described in the doc above.
- The dates and times need to be fixed.
- The survey-id needs to be the real thing for all responses.

Setup:

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE, eval = TRUE}

############### LOAD LIBRARIES AND PATHS #####################################

options(stringsAsFactors = FALSE)
github_base_path <- "https://raw.githubusercontent.com/PERTS/gymnast/master/"

tryCatch({
    source("~/Sites/gymnast/R/util.R")
    gymnast_install()
    source("~/Sites/gymnast/R/util_data_summaries.R")
    source("~/Sites/gymnast/R/util_qualtrics_cleaning.R")
    source("~/Sites/gymnast/R/util_graphing.R")
    source("~/Sites/gymnast/R/util_scale_computation.R")
    source("~/Sites/gymnast/R/util_dfc.R")
}, error = function(e){
    source(github_base_path %+% "R/util.R")
    source(github_base_path %+% "R/util_data_summaries.R")
    source(github_base_path %+% "R/util_qualtrics_cleaning.R")
    source(github_base_path %+% "R/util_graphing.R")
    source(github_base_path %+% "R/util_scale_computation.R")
    source(github_base_path %+% "R/util_dfc.R")
})

############### LOAD DATA #####################################

setwd("~/Sites/analysis/engagement_diagnostic/Creating EP 2018-2019 test data")

d_raw <- read.csv("ORIGINAL - Engagement_Project_OFFICIAL_20182019.csv")

d <- read.csv("ORIGINAL - Engagement_Project_OFFICIAL_20182019.csv") %>% qc.clean_qualtrics()

```

Fix survey ID:

```{r}

d$survey_id <- "Survey_n3PKCxt8"

```

Fix start-dates and end-dates:

```{r}

# Make total survey completion time an arbitrary 5 minutes (300 seconds)
d$Q_TotalDuration <- 300

# The intended fictional start and end dates are hidden in the value of the "testing" string. Use those.
d$StartDate[grep("week_8_6", d$testing)] <- "2018-08-06 13:26:47"
d$StartDate[grep("week_8_13", d$testing)] <- "2018-08-13 13:26:47"
d$StartDate[grep("week_8_20", d$testing)] <- "2018-08-20 13:26:47"
d$EndDate[grep("week_8_6", d$testing)] <- "2018-08-06 13:31:47"
d$EndDate[grep("week_8_13", d$testing)] <- "2018-08-13 13:31:47"
d$EndDate[grep("week_8_20", d$testing)] <- "2018-08-20 13:31:47"

# Confirm that all start and end dates have been changed
stopifnot(all(d$StartDate %in% c("2018-08-06 13:26:47", "2018-08-13 13:26:47", "2018-08-20 13:26:47")))
stopifnot(all(d$EndDate %in% c("2018-08-06 13:31:47", "2018-08-13 13:31:47", "2018-08-20 13:31:47")))


```

Fix participant IDs and tokens based on notes in GDoc linked in the intro.


```{r}

# token is classroom code + a number.
# using very rigid coding of row numbers here to confirm numbers of responses.

# Class_A1 "quick collard":
## Week 1:
### 1-20 (new)
d[d$StartDate %in% "2018-08-06 13:26:47" & d$code %in% "quick collard", "token"] <- "quick collard " %+% c(1:20)
## Week 2:
### 6-20 (old)
d[d$StartDate %in% "2018-08-13 13:26:47" & d$code %in% "quick collard" &
    d$first_login %in% "false", "token"] <- "quick collard " %+% c(6:20)
### 21-35 (new)
d[d$StartDate %in% "2018-08-13 13:26:47" & d$code %in% "quick collard" &
    d$first_login %in% "true", "token"] <- "quick collard " %+% c(21:35)
## Week 3:
### 6-35 (old)
d[d$StartDate %in% "2018-08-20 13:26:47" & d$code %in% "quick collard" &
    d$first_login %in% "false", "token"] <- "quick collard " %+% c(6:35)
### 36-40 (new)
d[d$StartDate %in% "2018-08-20 13:26:47" & d$code %in% "quick collard" &
    d$first_login %in% "true", "token"] <- "quick collard " %+% c(36:40)



# Class_B1 "peach turtle":
## Week 1:
### 1-20 (new)
d[d$StartDate %in% "2018-08-06 13:26:47" & d$code %in% "peach turtle", "token"] <- "peach turtle " %+% c(1:20)
## Week 2:
### 6-20 (old)
d[d$StartDate %in% "2018-08-13 13:26:47" & d$code %in% "peach turtle" &
    d$first_login %in% "false", "token"] <- "peach turtle " %+% c(6:20)
### 21-35 (new)
d[d$StartDate %in% "2018-08-13 13:26:47" & d$code %in% "peach turtle" &
    d$first_login %in% "true", "token"] <- "peach turtle " %+% c(21:35)
## Week 3:
### 6-35 (old)
d[d$StartDate %in% "2018-08-20 13:26:47" & d$code %in% "peach turtle" &
    d$first_login %in% "false", "token"] <- "peach turtle " %+% c(6:35)
### 36-40 (new)
d[d$StartDate %in% "2018-08-20 13:26:47" & d$code %in% "peach turtle" &
    d$first_login %in% "true", "token"] <- "peach turtle " %+% c(36:40)


# Class_B2 "turtle bronze":
## Week 1:
### 1-20 (new)
d[d$StartDate %in% "2018-08-06 13:26:47" & d$code %in% "turtle bronze", "token"] <- "turtle bronze " %+% c(1:20)


# Confirm that there is no more "test_token"
stopifnot(!"test_token" %in% d$token)

# Simply name participant IDs as "participant " + token
d$participant_id <- "participant " %+% d$token

```

"De-clean" the data back into weird original Qualtrics format and save result to CSV to be re-uploaded to Qualtrics.

```{r}

d_decleaned <- d
names(d_decleaned) <- names(d_raw)
d_decleaned <- rbind(d_raw[1, ], d_decleaned)

write.csv(d_decleaned, "MODIFIED - Engagement_Project_OFFICIAL_20182019.csv",
          na = "",
          row.names = FALSE)

```
